\section{Usability Testing}
ไหนลองเขียนบรรยายนิดนึงซิ
\subsection{Plan}
\begin{enumerate}
    \item \textbf{Product under test}
          \begin{itemize}
            \item What's being tested?
            \item What are the business and experience goals of the product
          \end{itemize}
    \item \textbf{Test objective}
          \begin{itemize}
              \item What are the goals of the usability test?
              \item What specific questions will be answered?
              \item What hypotheses will be tested?
          \end{itemize}
    \item \textbf{Participants}
          \begin{itemize}
              \item How many participants will be recruited?
              \item What are their key characteristics?
          \end{itemize}
    \item \textbf{Test task}
          \begin{itemize}
              \item What are the test task?
          \end{itemize}
\end{enumerate}
\subsection{Recruit}
\begin{enumerate}
    \item \textbf{Sreening}
          \begin{itemize}
            \item คุณสมบัติที่ต้องมี (Include)
            \item คุณสมบัติที่ไม่อยากได้ (Exclude)
          \end{itemize}
    \item \textbf{Schedule}
          \begin{itemize}
              \item ตารางนัดหมาย
          \end{itemize}
\end{enumerate}
\subsection{Prepare}
\begin{enumerate}
    \item \textbf{Prototype}
    \item \textbf{Task and scenario}
    \item \textbf{Facilitator script}
    \item \textbf{การวัดผลเชิงปริมาณ}
\end{enumerate}
\subsection{Conduct}
\begin{enumerate}
    \item \textbf{Facilitating}
    \item \textbf{Note Taking}
\end{enumerate}
\subsection{Analyze}
\begin{enumerate}
    \item \textbf{Gather issue lists from Usability test session.}
    \item \textbf{Group the same issue together (aka pattern).}
    \item \textbf{Create a theme.}
    \item \textbf{Prioritize findings and insights.}
    \item \textbf{Create recommendations.}
\end{enumerate}
